\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}

\begin{document}

\section*{GrapeExpectations --- Lean Startup Business Plan}

\subsection*{Identity}
GrapeExpectations provides vineyard block-scale sensing and analytics that reveal vine stress, water use, and spatial variability at block-to-row resolution. We combine distributed temperature sensing (DTS), remote sensing (NDVI), and data science to turn raw signals into actionable vineyard decisions.

\subsection*{Problem}
Growers lack continuous, spatially resolved insight into vine stress and water use. Point sensors, manual scouting, and periodic remote sensing are unreliable and costs scale super-linearly with vineyard size. This leads to inefficiencies and unwanted variability, particularly during critical phenological stages.
% Current tools such as spot sensors, manual scouting, and periodic imagery,are sparse, reactive, and poorly integrated. This leads to inefficient irrigation, yield variability, and quality risk, especially during critical phenological stages.

\subsection*{Our Solution}
GrapeExpectations deploys fiber-optic Distributed Temperature Sensing networks to measure meter-scale soil temperature continuously across entire vineyard blocks. These signals are fused with NDVI and weather data to produce simple, decision-ready outputs: irrigation guidance, stress maps, and anomaly detection tailored to vineyard operations.

\subsection*{Target Market}
The primary customers are commercial vineyard owners and managers, particularly mid-to-large operations where spatial variability materially impacts yield and quality. 

\subsection*{The Competition}
Existing solutions include spot-based soil moisture probes, drone and satellite NDVI providers, and general-purpose environmental sensor vendors. While each addresses part of the problem, none provide continuous spatial coverage integrated into a vineyard-specific decision framework. GrapeExpectations differentiates by combining continuous sensing with viticulture-native analytics.

\subsection*{Revenue Streams}
Revenue will be generated through sensing-as-a-service offerings, including seasonal or annual monitoring contracts, paid pilot deployments priced per block or per acre, and recurring subscriptions for ongoing analytics access. Optional consulting services will support vineyard design, deployment strategy, and interpretation.

\subsection*{Marketing Activities}
Initial growth will be driven by direct outreach to vineyard managers and growers, pilot projects demonstrating return on investment through water savings and yield stability, and industry referrals. Technical whitepapers, conference presentations, and professional introductions will establish credibility and trust.

\subsection*{Expenses}
Key expenses include fiber-optic cable and DTS interrogator access, installation and field deployment labor, data infrastructure and analysis tooling, travel, insurance, and basic operating and legal costs.

\subsection*{Team and Key Roles}
GrapeExpectations is founder-led. Core responsibilities include data science and modeling, sensing system design and deployment, and customer-facing interpretation and decision support. As the business scales, future hires will focus on deployment execution and customer success.

\subsection*{Milestones}
Near-term milestones include completing the first paid pilot deployment, demonstrating measurable improvements in irrigation efficiency or grape quality, securing the first recurring vineyard contract, and expanding to multi-block or multi-site deployments.

\end{document}
